---
title: "What is Reproducibility?"
subtitle: "TIES 2023 Reproducibility Workshop"  
author: 
  - "Wesley Burr (Trent)"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: '%current%'
      titleSlideClass: [top, left]
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, 
                      echo = FALSE, 
                      warning = FALSE,
                      fig.align = "center")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#9F999C",
  secondary_color = "#FFE5F3",
  inverse_header_color = "#8F8C8E",
  link_color = "deeppink",
  title_slide_text_color = "#3d3d3d",
  title_slide_background_image = "img/title-slide-background-light.png",
  title_slide_background_position = "left",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

class: center, middle

# Background: Reproducibility

```{r include=FALSE}
library(ggplot2)
filter <- dplyr::filter
knitr::opts_chunk$set(warning=FALSE, message=FALSE, fig.width=10.5, fig.height=4, 
  comment=NA, rows.print=16)
#theme_set(theme_gray(base_size = 24))
```

---

## Reproducibility 

In this workshop, we are specifically interested in discussing ways in which to encourage
students (and professionals, and faculty!) to develop skills and habits for strong
reproducible research *methods*, particularly with 
respect to their data gathering, manipulation, and analysis. 

---

## Reproducible Research Methods

The first published work we are aware of that discusses the specific framework we are
thinking of (computational reproducibility) is 1990-92, J. Claerbout 
at Stanford:

<br/>

**J. Claerbout, M. Karrenbach**, *Electronic documents give reproducible research a new meaning*, in Proceedings of the 62nd Annual International Meeting of the Society of Exploration Geophysics, New Orleans, USA, 25 to 29 October 1992.

( referenced by David Donoho in [1995](http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.53.6201) )
---

class: inverse

## Reproducible Research Methods

Some quotes:

<br/>
- a revolution in education and technology transfer follows from the marriage of word processing and software command scripts

--

- researchers ... can reproduce their own research results a year or more later by "pressing a single button"

--

- Our basic goal is reproducible research. The electronic document is our means to this end

--

<br/>
https://doi.org/10.1190/1.1822162

---

## Definition

<br/>
... the idea that scientific results should be documented in such a way that their deduction is fully transparent. This requires a detailed description of the methods used to obtain the data and making the full dataset and the code to calculate the results easily accessible.
**This is the essential part of open science.**

<br/>
*Wikipedia, https://en.wikipedia.org/wiki/Reproducibility*

---

## Some Necessary Components

To make any research project **computationally** reproducible

- all data and files should be clearly: separated; labelled; documented
    
--

- all operations should be automated as much as practicable, avoiding manual intervention 

--

- workflow should be designed as a sequence of steps (**scripts!**), combined so intermediate outputs from one step directly feed in as inputs to the next

--

- version control should be used

---

## Workflow Includes

- data acquisition

--

- data processing
    - entry
    - manipulation
    - filtering

--

- data analysis
    - computation of statistics
    - figures
    - model-fitting (including interim steps!) - avoid The Garden of Forking Paths!
    - linear flow, resist urge to modify earlier steps (HARKing)

---

## Researcher Point of View

I  strongly endorse **Data Carpentry**, a program of workshops teaching scientists
basic skills in this sort of thinking.

<br/>
If you do this kind of process for your research (and if you do statistics
as a primary focus, or as a tool in your research,  you *should*!), to do that
research properly, you have to know how to do this kind of thing!

<br/>
*Medice, cura te ipsum (Physician, heal thyself)*

<br/>
https://datacarpentry.org/

---

class: inverse

## Some Good References to Get Started

Materials for a 3-hour Workshop on R Markdown: [R Markdown Training](https://hbctraining.github.io/Training-modules/Rmarkdown/) <br/>
The Data Carpentry Initiative: [Data Carpentry](https://datacarpentry.org/) <br/>
A Coursera Course: [Reproducible Research with R Markdown](https://www.coursera.org/learn/reproducible-research) <br/>
The Book: [R Markdown, the Definitive Guide](https://bookdown.org/yihui/rmarkdown/) <br/>

<br/>&nbsp;<br/>

[Reproducible Science Curriculum](https://github.com/Reproducible-Science-Curriculum/)<br/>
Drs. Goodman, Fanelli, Ioannidis [What does research reproducibility mean?](https://stm.sciencemag.org/content/8/341/341ps12#ref-4)<br/>
IEEE [Special Issue on Reproducible Research](https://ieeexplore.ieee.org/document/4720217)<br/>
[Reproducible Science Curriculum](https://github.com/Reproducible-Science-Curriculum/)<br/>
Dr. Mine Çetinkaya-Rundel, [Teaching R, 5 Principles](https://mine-cetinkaya-rundel.github.io/2021-teach-r-five-principles-liverpool/)<br/>

---

class: inverse

## Some Newer References (last 18 months)

* [Building Reproducible Analytical Pipelines with R](https://leanpub.com/raps-with-r/)
    - book also available for [free](https://raps-with-r.dev/)
    - some [slides](https://64a7f00fce57ea61a8302dd5--stellar-bublanina-8574b2.netlify.app/#/title-slide) talking about this book and its themes
* [The five pillars of computational reproducibility](https://osf.io/4pd9n/)

Some good posts talking about issues raised today:
* [renv, Docker, and GitHub Actions](http://haines-lab.com/post/2022-01-23-automating-computational-reproducibility-with-r-using-renv-docker-and-github-actions/)
* [Perspective from a psychologist, organizing his lab](https://www.lornecampbell.org/?p=171)
* [Some good practices for research with R](https://www.good-practices.etiennebacher.com/#/title-slide)

A good course, all on GitHub, that can take you much deeper:
* [Course from JHU School of Public Health](https://www.stephaniehicks.com/jhustatprogramming2022/schedule)